### 2018-05-22 FrascatiPlot/Paper/NucleiB2.tex
adding a lot of text

For the table: there seems to be a nice summary here (including that the hyper-triton is spin 1/2):
https://books.google.fr/books?id=utBKDwAAQBAJ&pg=PA56&lpg=PA56&dq=spin+of+hypertriton&source=bl&ots=x-wqVWSIpJ&sig=k2tZUsruf2M5o-slqOp0Q9v-PCI&hl=de&sa=X&ved=0ahUKEwj1-NOo4t3aAhUCU1AKHbjVCAoQ6AEIczAJ#v=onepage&q=spin%20of%20hypertriton&f=false
Properties And Interactions Of Hyperons - Proceedings Of U.s.-japan Seminar
herausgegeben von Barnes Peter D,Nakai K,Gibson Benjamin F

@@

\subsection{Source volume}
As in \cite{Scheibl:1998tk}, we identify the source volume as the effective sub-volume of the whole system which is governed by the homogeneity length of the interacting nucleons. In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation. As discussed in Appendix \ref{appendix1}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$, thus $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.

@@

Nuclei form at chemical freeze-out and their yields are determined only by mass and chemical freeze-out temperature:  dN/dy ~ exp (-m/Tch)
pT spectra have been modeled with a Blast-Wave parameterization, with params. fixed by fit to ?,K,p

Normalisation for the spectra is fixed to the d/? (3He/?) ratio from thermal model times the measured ? yield.

Normalisation for 3LH is extracted from the 3He and the S3 predicted by thermal model

\section{Comparison with experimental data}\label{sec:comparison}
- excess binding energy needs to be released to the system to make coalescence work

>>>>

For the table: there seems to be a nice summary here (including that the hyper-triton is spin 1/2):
%https://books.google.fr/books?id=utBKDwAAQBAJ&pg=PA56&lpg=PA56&dq=spin+of+hypertriton&source=bl&ots=x-wqVWSIpJ&sig=k2tZUsruf2M5o-slqOp0Q9v-PCI&hl=de&sa=X&ved=0ahUKEwj1-NOo4t3aAhUCU1AKHbjVCAoQ6AEIczAJ#v=onepage&q=spin%20of%20hypertriton&f=false
Properties And Interactions Of Hyperons - Proceedings Of U.s.-japan Seminar
herausgegeben von Barnes Peter D,Nakai K,Gibson Benjamin F

@@

\subsection{Source volume}
\label{SecSourceVolume}
As in \cite{Scheibl:1998tk}, we identify the source volume as the effective sub-volume of the whole system which is governed by the homogeneity length of the interacting nucleons. In addition, the same authors claim that this volume is experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry. 
The experimental results are typically obtained following the Bertsch-Pratt (BP) parameterisation ($R_{out}, R_{side}, R_{long}$), while the coalescence model described in Section \ref{sec:coalescence} expresses the volume in terms of the Yano-Koonin-Podgoretskii (YKP) parameterisation. As discussed in Appendix \ref{appendix1}, we identify $\rperp = R_{side}$ and $\rpar = R_{long}$, thus $R = (\rperp^{2}\rpar)^{1/3} \approx (R_{side}^{2}R_{long})^{1/3}$.

@@

In the statistical-thermal approach, the yields (d$N$/d$y$) of light anti- and hyper-nuclei are very sensitive to the chemical freeze-out temperature $T_{chem}$ due to their large mass $m$ and approximately scale as d$N$/d$y \propto \exp(-m/T_{chem})$. As a matter of fact, the chemical freeze-out temperature defines the only scale in this model, since at the LHC the chemical potentials which ensure the conservation of baryon number ($\mu_{B}$), strangeness ($\mu_{S}$), and electric charge ($\mu_{Q}$) are negligible.
In contrast to the coalescence approach, the current implementations~\cite{} of the statistical-thermal model provide only \pt-integrated yields and not the full hadron spectra. 
In order to fill this gap, and for the purposes of this exercise, \pt~spectra have been modeled using a blast-wave~\cite{} parameterization. When extracting the predicted spectrum for a given particle species (proton, $\Lambda$, deuteron, \hethree), the parameters of the blast-wave (average radial flow velocity $\langle\beta_{T}\rangle$, kinetic freeze-out temperature $T_{kin}$, and velocity profile $n$) are fixed to the values obtained from the simultaneous fit of the pion, kaon and proton spectra measured in each collision system and multiplicity event class by ALICE~\cite{}. 
The normalisation is fixed using the \pt-integrated deuteron-to-pion ratio and \hethree-to-pion ratio predicted by the GSI-Heidelberg model with $T_{chem} = 156$ MeV, multiplied by the pion yield measured by ALICE~\cite{}. 
This choice is motivated by the fact that the measured proton yield is seen to be slightly underestimated by the thermal model predictions at the LHC~\cite{}.
In the case of hyper-triton, a slightly different procedure is chosen, namely the normalisation for \hthreelambda~is extracted from the statistical-thermal model prediction of the strangeness population factor $S_{3}$ multiplied by the measured $\Lambda/p$ ratio \cite{} and the measured \hethree~yield \cite{}. Based on the thus obtained spectra, we calculate the corresponding coalescence parameters for a given \pt/A and compare it with coalescence expectations. Because we use experimental data to constrain the blast-wave prediction as well as the normalisation, and because such data are provided for given centrality/multiplicity classes, we use the corresponding \avdNdeta~in the same class to estimate the system radius based on the parameterisation discussed in Sec.~\ref{SecSourceVolume}. 
In contrast to the coalescence approach which explicitly depends on the size of the produced object with respect to the system size, the object size does not enter in the formulation of the blast-wave model, which as a simplified hydrodynamic model treats the system based as a continuum and is not particle based. The thermal model on the other hand, implements eigenvolume corrections where the object radius is fixed as an external parameter ($r=0.3$~fm in the case of baryons for the GSI-Heidelberg prediction used here). We refer to the literature for the extensive discussions on the validity of the eigenvolume correction for light anti- and hyper-nuclei~\cite{Volodya} and the relation with the possible production of these objects as compact quark bags~\cite{Andronic:2017}.

\section{Comparison with experimental data}\label{sec:comparison}

Data on anti- and hyper-nuclei production at LHC energies and different collision systems have been released by the ALICE Collaboration in recent years \cite{}. 
In Fig. \ref{} we compare the coalescence parameter \btwo~from the coalescence model (see Eqs.~\ref{eq:B2cd} and \ref{eq:B2approx}, with $r_{d} = 3.2$ fm) with the ALICE data.  
First, the parameterisation of the system radius fitted to the HBT data as described in Sec.~\ref{SecSourceVolume} is used to map the \avdNdeta~to the source size (datapoints shown with \textcolor{red}{empty markers}).
We notice already at this point that the coalescence volume from our extracted parameterisation of the HBT radii leads to discrepancies with respect to the curve from the coalescence calculation, and in particular, we notice that the model would require a larger radius for a given value of \btwo.
Therefore, in a second step the radius is tuned such that the data points for (anti-) deuterons fall onto the coalescence prediction (solid markers). We find that the parameters of Eq.~\ref{eq:radiusParameterisation} turn out to be \textcolor{red}{$a = xxx$ and $b = yyy$}. 
With this second parameterisation, we investigate also the agreement of the model with the measured coalescence parameter \bthree. As shown in Fig.~\ref{}, also in the case of \bthree, a tension between the model and the data is found which persists with both parameterisations.
It is also noteworthy that any change of the radii parameterisation would result in a shift along the x axis of both \btwo~and \bthree~data points in the same way, while the theoretical coalescence curve would not be affected.

- discuss sensitivity to the choice of the kT for the radii parameterisation.

- add a plot with different radii for hyper-triton from 10fm to 3fm

- add a plot for A=4

- add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
